### 2020-07-01 abstract.tex

\begin{abstract}
\label{abstract}
We use smartphones everywhere and privacy concerns have arisen for the ``shoulder surfing'' attack, where strangers peek at our phone in public areas. To mitigate this privacy threat, various countermeasures have been designed but mainly against attackers with the naked eye. With the development of smartphones and super resolution (SR) technique, a malicious attacker can peek from farther away with the assist of his/her smartphone camera and SR algorithms, rendering the underestimated threat model. To underline this concern, we present \textsf{SRPeek}, an end-to-end system of shoulder surfing deployed on commercial smartphones, including a unique deep neural network (DNN) architecture for multi-image SR. We implement \textsf{SPPeek} in Android. The experimental results demonstrate its efficiency and robustness, allowing a human to read 90\% of the characters at a distance of 1.8m with traditional lenses and 6m with optical zooming lenses. And it outperforms the state-of-the-arts and fills the blank space of multi-image SR for shoulder surfing attack.
\end{abstract}

>>>>

\begin{abstract}
\label{abstract}
We use smartphones everywhere and privacy concerns have arisen for the ``shoulder surfing'' attack, where strangers peek at our phone in public areas. To mitigate this privacy threat, various countermeasures have been designed but mainly against attackers with the naked eye. With the development of smartphones and super resolution (SR) technique, a malicious attacker can peek from further away with the assist of his/her smartphone camera and SR algorithms, rendering the underestimated threat model. To underline this concern, we present \textsf{SRPeek}, an end-to-end system of shoulder surfing deployed on commercial smartphones, including a unique deep neural network (DNN) architecture for multi-image SR. We implement \textsf{SPPeek} in Android. The experimental results demonstrate its efficiency and robustness, allowing a human to read 90\% of the characters at a distance of 1.8m with traditional lenses and 6m with optical zooming lenses. And it outperforms the state-of-the-arts and fills the blank space of multi-image SR for shoulder surfing attack.
\end{abstract}

### 2020-07-01 evaluation.tex

\section{Evaluation \& Case Study}
\label{sec-evaluation}
% \begin{figure*}[!t]
%     \centering
%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1.pdf}\label{fig-control-1}}
%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1_2.pdf}\label{fig-control-2}}
%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2.pdf}\label{fig-random-1}}
%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
%     \hfill
%     \caption{Performance in Controlled Environment (a,b) and Random Environment (c,d).}
%     \label{fig-performance-1}
% \end{figure*}
We evaluate the ability of the network model, testing its performance in different training and testing conditions. We perform the following experiments with two phones: a Redmi 6A smartphone, with a single rear camera with 13 million pixels and digital zoom only, and a HUAWEI P40 Pro, with multiple rear cameras, the telephoto camera(which we use in the experiments) possessing up to 5x optical zooming ability which we will utilize fully in our experiments. 
\subsection{Performance In Controlled Environment}
We train and test the model with the images captured with exactly the same environment parameters, and used Peak Signal to Noise Ratio to evaluate the accuracy of the recovered images(see Figure~\ref{fig-control-1} and Figure~\ref{fig-control-2}). Moreover, the ultimate goal of our system is the readability of the recovered images, so we also used Optical Character Recognition(OCR) services to evaluate the accuracy. The model with traditional lenses(without optical zoom) is trained and tested at 1~2 meters range, while the one with optical zoom at 5~7.5 meters, at which distance less than 5\% of the characters(only the simplist ones) can be recognized by humans from the photos without the assistance of SR algorithms. The model can achieve an accuracy above 90\% at 1.8m with traditional lenses and 6m with optical zooming lenses. Considering the complexity of Chinese characters, and the assist of context when read by an OCR recognizer, we believe this level of accuracy can provide sufficient data at a shoulder surfing scenario, thus proving the efficiency of our model.
\begin{figure}[!t]
    \centering
    \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_1.pdf}\label{fig-control-1}}
    \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_1_2.pdf}\label{fig-control-2}}
    \hfill
    \caption{Performance in Controlled Environment using Traditional Lens and Optical Lens.}
    \label{fig:control}
\end{figure}

In the optical zoom group the accuracy of the model dropped drastically at 7m distance. Increased distances means less data and less restrictions of the possible outputs, which leads to artifacts(missing or misplaced strokes,etc.). It's the nature of Chinese characters that one mistaken stroke will largely affect its readability, leading to the result that while the pixelwize error rises steadily with the increased distance, the accuracy will experience a drastic drop.

\subsection{Performance In Random Environment}
We train the model with data captured in different environments, as mentioned before, and test its ability in other environments(see Figure~\ref{fig-random-1} and Figure~\ref{fig-random-2}). The model achieves an accuracy above 90\% at 1.8m with traditional lenses and 6m with optical zooming lenses. 
\begin{figure}[!t]
    \centering
    \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_2.pdf}\label{fig-random-1}}
    \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
    \hfill
    \caption{Performance in Random Environment using Traditional Lens and Optical Lens.}
    \label{fig:control}
\end{figure}

@@

\subsection{Adapting Ability}
We train the model with fewer groups of data, exposing it to fewer variations of environment parameters, and examine the model’s performance in other environments. The results are shown in Figure~\ref{fig-adapt-tranditional}.Only the results from the traditional lenses is shown, as the optical zoom lenses group face longer distances and more complex distortions, and with incomplete data the model fails to manage any reasonable reconstruction on the test dataset, resulting in extremely low accuracy in all experiments.
\begin{figure}[!t]
    \centering
    \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_3.pdf}\label{fig-adapt-tranditional}}
    \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_4.pdf}\label{fig-adapt-optical}}
    \hfill
    \caption{Performance for Adapting Ability using Traditional Lens and Optical Lens.}
    \label{fig:adapting}
\end{figure}

>>>>

\section{Evaluation and Case Study}
\label{sec-evaluation}
% \begin{figure*}[!t]
%     \centering
%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1.pdf}\label{fig-control-1}}
%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1_2.pdf}\label{fig-control-2}}
%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2.pdf}\label{fig-random-1}}
%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
%     \hfill
%     \caption{Performance in Controlled Environment (a,b) and Random Environment (c,d).}
%     \label{fig-performance-1}
% \end{figure*}
We evaluate the performance of the network model in different training and testing conditions. We perform the following experiments with two COTS smartphones: a Redmi 6A smartphone, with a single rear camera with 13 million pixels and digital zoom only, and a HUAWEI P40 Pro, with multiple rear cameras. The telephoto camera possesss up to 5x optical zooming ability which we will utilize fully in our experiments.

\begin{figure}[!t]
    \centering
    \subfigure[Traditional Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_1.pdf}\label{fig-control-1}}
    \subfigure[Optical Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_1_2.pdf}\label{fig-control-2}}
    \hfill
    \caption{Performance in Controlled Environment using Traditional Lens and Optical Lens.}
    \label{fig:control}
\end{figure}

\subsection{Performance In Controlled Environment}
In these experiments, we train and test the model with the images captured with exactly the same environment parameters, and used Peak Signal to Noise Ratio to evaluate the accuracy of the recovered images. The results are shown in Figure~\ref{fig-control-1} and Figure~\ref{fig-control-2}. Moreover, the ultimate goal of our system is the readability of the recovered images, so we also used Optical Character Recognition(OCR) services to evaluate the accuracy. The model with traditional lenses (without optical zoom) is trained and tested at 1-2 meters range, while the one with optical zoom at 5-7.5 meters, at which distance less than 5\% of the characters (only the simplest ones) can be recognized by humans from the photos without the assistance of SR algorithms.

From Figure~\ref{fig-control-1}, we can see the model can achieve an OCR accuracy above 90\% at 1.8m with traditional lenses in both day and night time. The PSNR is higher than 10 as well. The OCR accuracy and PSNR drops in night time since the darker environmental lighting condition as well as with the increasing of distance since the longer distance means more blurs. For Figure~\ref{fig-control-2}, we can see the OCR accuracy is larger than 90\% at 6m with optical zooming lenses. The performance is relatively consistent in both day and night time. Considering the complexity of Chinese characters, and the assist of context when read by an OCR recognizer, we believe this level of accuracy can provide sufficient data at a shoulder surfing scenario, thus proving the efficiency of our model.

In the optical zoom group, the accuracy of the model dropped drastically at 7m distance. Increased distances means less data and less restrictions of the possible outputs, which leads to artifacts(missing or misplaced strokes, etc.). It is the nature of Chinese characters that one mistaken stroke will largely affect its readability, leading to the result that while the pixel-wise error rises steadily with the increased distance, the accuracy will experience a drastic drop.

\subsection{Performance In Random Environment}
We train the model with data captured in different environments, as mentioned before, and test its ability in other environments. The results are shown in Figure~\ref{fig-random-1} and Figure~\ref{fig-random-2}. For Figure~\ref{fig-random-1}, the model can still achieve an OCR accuracy above 85\% at 1.8m with traditional lenses. From Figure~\ref{fig-random-2}, the OCR accuracy keeps higher than 90\% at 6m with optical zooming lenses. This verifies the efficiency of our model for environment adaption.

\begin{figure}[!t]
    \centering
    \subfigure[Traditional Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_2.pdf}\label{fig-random-1}}
    \subfigure[Optical Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
    \hfill
    \caption{Performance in Random Environment using Traditional Lens and Optical Lens.}
    \label{fig:control}
\end{figure}

@@

\subsection{Adapting Ability}
We train the model with fewer groups of data, exposing it to fewer variations of environment parameters, and examine the model's performance in other environments. The results are shown in Figure~\ref{fig-adapt-tranditional}. Only the results from the traditional lenses is shown, as the optical zoom lenses group face longer distances and more complex distortions, and with incomplete data the model fails to manage any reasonable reconstruction on the test dataset, resulting in extremely low accuracy in all experiments.
\begin{figure}[!t]
    \centering
    \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_3.pdf}\label{fig-adapt-tranditional}}
    \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_4.pdf}\label{fig-adapt-optical}}
    \hfill
    \caption{Performance for Adapting Ability using Traditional Lens and Optical Lens.}
    \label{fig:adapting}
\end{figure}
